Manhattan Plot

### 2021-09-24 code/manhattan_animated.Rmd
fixed errors relative to shapes

fig = data %>%
  mutate(shape = if_else(OR > 1, 0, 1)) %>%
  # filter(week == 33) %>%
  # arrange(OR) %>%
  # mutate(pos2 = row_number()) %>%
  # select(Variable, pos) %>%
  # inner_join(data) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    alpha = 0.75,
    symbol = ~shape,
    symbols = c(220, 219),
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
fig
```

@@

fig = data %>%
  mutate(shape = if_else(OR > 1, 220, 219)) %>%
  # filter(week == 33) %>%
  # arrange(OR) %>%
  # mutate(pos2 = row_number()) %>%
  # select(Variable, pos) %>%
  # inner_join(data) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    symbol = ~shape,
    symbols = c(220, 119),
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(scene = list(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
fig
```

@@

fig = data %>%
  mutate(shape = if_else(OR > 1, 0, 1)) %>%
  # filter(week == 33) %>%
  # arrange(OR) %>%
  # mutate(pos2 = row_number()) %>%
  # select(Variable, pos) %>%
  # inner_join(data) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    alpha = 0.75,
    symbol = ~shape,
    symbols = c(220, 219),
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
fig
```

@@

>>>>

fig = data %>%
  mutate(shape = if_else(OR > 1, 0, 1)) %>%
  # filter(week == 33) %>%
  # arrange(OR) %>%
  # mutate(pos2 = row_number()) %>%
  # select(Variable, pos) %>%
  # inner_join(data) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    alpha = 0.75,
    symbol = ~shape,
    symbols = c(219, 220),
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
fig
```

@@

fig = data %>%
  mutate(shape = if_else(OR > 1, 220, 219)) %>%
  # filter(week == 33) %>%
  # arrange(OR) %>%
  # mutate(pos2 = row_number()) %>%
  # select(Variable, pos) %>%
  # inner_join(data) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    symbol = ~shape,
    symbols = c(219, 220),
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(scene = list(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
fig
```

@@

fig = data %>%
  mutate(shape = if_else(OR > 1, 0, 1)) %>%
  # filter(week == 33) %>%
  # arrange(OR) %>%
  # mutate(pos2 = row_number()) %>%
  # select(Variable, pos) %>%
  # inner_join(data) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    alpha = 0.75,
    symbol = ~shape,
    symbols = c(219, 220),
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  ) %>%
  layout(
    xaxis = list(title = "Variable"),
    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
fig
```

<!-- === -->
```{r, eval = F}
vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "31", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
      mutate(codgeo = as.factor(commune_residence)) %>%
      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "31", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
      mutate(codgeo = as.factor(epci)) %>%
      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
      plyr::rbind.fill(vacc_com)

test = vacc %>% inner_join(LOG_fact %>%
                      select(codgeo, Overcrowding_rate)) %>%
  mutate(taux_1_inj = binarisation(as.numeric(taux_1_inj), 0.25))

summary(test$Overcrowding_rate)
summary(test$taux_1_inj)
```

<!-- === -->

@@

```{r, eval = F}
data = NULL
for (i in 2:last_week){
  data = bind_rows(
    data,
    make_data_covid(i) %>%
      arrange(theme, id) %>%
      mutate (pos = row_number(),
              week = i)
  )
}
```

```{r, eval = F}
data1 = data
```

```{r, eval = F}
data = data1 %>%
  # filter(Variable %in% c("NO-SE",
  #                        "Overcrowding_rate",
  #                        "Interdecile_91_Ratio",
  #                        "Unemployment_Benef",
  #                        "Immigrant",
  #                        "Pop_NoChildFamily_HH")) %>%
  filter(week >= 22) %>%
  mutate(ban = as.factor(if_else(week <27, 0, 1)))
p = data %>%
  # filter(ban == 0) %>%
  ggplot() +
  aes(x = week, y = log(`max_OR-inv_OR`), color = Variable, alpha = 0.5) +
  geom_point(size = 0.5) +
  # geom_vline(aes(xintercept = 26.5)) +
  geom_smooth(aes(fill = ban), size = 0.5, method = "lm", se = F)+
  theme_bw() +
  theme(legend.position = "none") 
# ggplotly(p)

# plot(data$`max_OR-inv_OR`,
#      type="n",
#      ylim=c(00,12),
#      xlab="Week",
#      ylab="log(Interdecile_91_Ratio)",
#      bty="l",
#      xaxt="n")
# rect(26.5,0,34,12,col=grey(0.9),border=F)
# points(log(data$`max_OR-inv_OR`[data$ban==0]),cex=0.7)
```
